MS&E 226: Project Part 1 Code

### 2024-12-02 MS&E 226_Project Part 2_Code.Rmd
OLS on Lasso covariates

@@

#### (c)

@@

# Identify numeric predictors
numeric_predictors <- sapply(df_pred[predictor_columns], is.numeric)

>>>>

```{r create OLS model using covariates selectedin Lasso}

# Generate the final Lasso model

# Extract predictors (X) and response variable (y) for the train set
X_train <- model.matrix(Log_Revenue_Total ~ ., data = df_pred)[, -1]
y_train <- df_pred$Log_Revenue_Total

# Refit the Lasso model on the test set using the final lambda from training
final_lasso_model <- glmnet(X_train, y_train, alpha = 1, lambda = final_lambda_lasso, standardize = TRUE)

# Extract non-zero coefficients from the final Lasso model
lasso_coefficients <- coef(final_lasso_model)
lasso_coefficients <- as.matrix(lasso_coefficients)  # Convert to a matrix
nonzero_covariates <- rownames(lasso_coefficients)[lasso_coefficients != 0]
nonzero_covariates <- nonzero_covariates[nonzero_covariates != "(Intercept)"] # Exclude intercept

# Identify all one-hot encoded categorical variables in this list and remove all but one
remove_after_capital <- function(x) {
  # Use a regular expression to find a lowercase letter followed by an uppercase letter
  gsub("([a-z])[A-Z].*", "\\1", x)
}

# Apply the function to the vector of strings
unique_nonzero_covariates <- sapply(nonzero_covariates, remove_after_capital)

# Print the modified strings
print(unique_nonzero_covariates)

# Identify unique strings (appear exactly once)
unique_nonzero_covariates <- names(table(unique_nonzero_covariates)[table(unique_nonzero_covariates) == 1])

# Print the unique strings
print(unique_nonzero_covariates)

# Subset the dataframe with the selected covariates
df_selected <- df_pred[, c("Log_Revenue_Total", unique_nonzero_covariates)]

# Create the formula for OLS regression
ols_formula <- as.formula(paste("Log_Revenue_Total ~", paste(unique_nonzero_covariates, collapse = " + ")))

# Run the OLS regression
ols_train <- lm(ols_formula, data = df_selected)

# Print summary of the OLS regression model
summary(ols_train)

@@

#### (c)
```{r 2c Fit to test data OLS}

# Refit the OLS model on the test set 
ols_test <- lm(ols_formula, data = df_test)

# Extract coefficients from the test set
ols_test_coefs <- coef(ols_test)

# Extract coefficients from training and holdout models
training_coefs <- as.matrix(coef(ols_train))
holdout_coefs <- as.matrix(ols_test_coefs)

```{r 2d bootstrap OLS}

# Identify numeric predictors
numeric_predictors <- sapply(df_pred[column_names], is.numeric)

@@

# Identify numeric predictors
numeric_predictors <- sapply(df_pred[column_names], is.numeric)
